Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-02-08 constantRate/ConstCompFuzzExt.tex
abstract v2

\begin{abstract}
Fuzzy extractors derive strong keys from noisy sources.  The goal is to reliably convert a high entropy source~(which may differ on repeated readings) to the same uniformly distributed key.  Traditionally, their security is defined information-theoretically.  %Fuzzy extractors have upper bounds on the length of the derived key.

Fuzzy extractors work for any distribution with enough entropy.  %In this setting, the entropy of the source must be significantly higher than the logarithm of number of error patterns corrected~(Dodis et al., J. of Comp 2008).
We call the difference between the starting entropy and the logarithm of the number of correctable error patterns the \emph{minimum usable entropy}.  Dodis et al.~(J. of Comp. 2008) show there is some source where the key length cannot exceed the minimum usable entropy.  Therefore, fuzzy extractors that output the same length key for any source with enough entropy cannot output a key longer than the minimum usable entropy.
For many practical noisy sources, like biometrics, the minimum usable entropy is negative, leaving reliable key derivation from these sources as an open problem.

@@

Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$.
We need a strong version of point obfuscation that remains secure even when several obfuscations of correlated points are composed. While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}. For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions. Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}. We note that the problem of fuzzy extractors remains non-trivial even given the recent progress on general purpose obfuscation \cite{GargGH0SW13,BrakerskiR13,BarakGKPS13}, as the achieve notions of obfuscation seem to be insufficient.

>>>>

\begin{abstract}
Fuzzy extractors convert a noisy source of entropy into a consistent uniformly distributed key.  In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of correctable error patterns. We call what is left after this worst-case loss the \emph{minimum usable entropy}.  Unfortunately, this quantity is negative for some sources that are important in practice.

We construct fuzzy extractors with computational security that work for distributions in which the minimum usable entropy is negative. They correct Hamming errors over a large alphabet. In order to avoid the worst-case loss, they necessarily restrict distributions for which they work.  Our first construction requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.  Our second construction requires  a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols. The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.

\iffalse
For many practical noisy sources, like biometrics, the minimum usable entropy is negative, leaving reliable key derivation from these sources as an open problem.

Traditionally, their security is defined information-theoretically.  %Fuzzy extractors have upper bounds on the length of the derived key.

Fuzzy extractors work for any distribution with enough entropy.  %In this setting, the entropy of the source must be significantly higher than the logarithm of number of error patterns corrected~(Dodis et al., J. of Comp 2008).

We call the difference between the starting entropy and the logarithm of the number of correctable error patterns the \emph{minimum usable entropy}.  Dodis et al.~(J. of Comp. 2008) show there is some source where the key length cannot exceed the minimum usable entropy.  Therefore, fuzzy extractors that output the same length key for any source with enough entropy cannot output a key longer than the minimum usable entropy.

@@

Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$.
We need a strong version of point obfuscation that remains secure even when several obfuscations of correlated points are composed. While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}. For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions. Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}. We note that the problem of fuzzy extractors remains non-trivial even given the recent progress on general purpose obfuscation \cite{GargGH0SW13,BrakerskiR13,BarakGKPS13}, as the achieved notions of obfuscation seem to be insufficient.
